Title here

### 2016-09-19 portfolio/text/ms.Rmd
update

- What's novel
    - Huge dataset
    - Permit level data
    - Account for covariates
    - Accounting for strategies
    - Keeping annual data (not condensing to mean and cv)
    - Joint modelling
    - look at different mechanisms of diversification
- Suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost 
- Adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next
- not as simple as increase diversity (within permit) and reduce risk
- 2 dimensions to think about (revenue and variability); and the trade-off is fishery specific 
    - effects within a permit strategy are permit specific  
    - Importantly it's a tradeoff - 2 dimensions - sometimes make more money by specializing... Some highly variable single species permits make a ton of money... which preferable?

@@

- How fit in with K and H?
- Year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional diversification
- Risk results not really risk, but unpredictability given our covariates ...
don't change anything and it's most predictable how well you'll do
- What's unpredictable in our model, might be more predictable on a year to
year, species by species basis for individual permit holder
- Equilibrium, average variability vs year to year effect for one person

>>>>

- What's novel
    - Huge dataset
    - Permit level data (on individuals, not vessels)
    - Account for covariates
    - Accounting for strategies
    - Keeping annual data (not condensing to mean and cv)
    - Joint modelling of mean and variance
    - look at different mechanisms of diversification
- Suggests it's mostly an across strategy/permit effect (lowering variability),
  which isn't always a possibility because of regulations and cost 
- Adjusting within current permit constraints is risky... Not clearly risk
  reducing to generalize from one year to the next
- not as simple as increase diversity (within permit) and reduce risk
- 2 dimensions to think about (revenue and variability); and the trade-off is fishery specific 
    - effects within a permit strategy are permit specific  
    - Importantly it's a tradeoff - 2 dimensions - sometimes make more money by specializing... Some highly variable single species permits make a ton of money... which preferable?

@@

- How fit in with K and H?

EW: part of the difference is individuals vs vessels. For example, K&H suggested that diversity declined following IFQs for halibut sablefish vessels. The reason for the decline was that the vessels were allowed to fish halibut for more days (because people were sharing boats). At the level of people, we wouldn't expect the diversity of someone who only had halibut/sablefish permit to be affected by IFQs. The person, not the vessel holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq

- Year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional diversification (unless you have a M or salmon permit)
- Risk results not really risk, but unpredictability given our covariates ...
don't change anything and it's most predictable how well you'll do
- What's unpredictable in our model, might be more predictable on a year to
year, species by species basis for individual permit holder
- Equilibrium, average variability vs year to year effect for one person
